### 2017-04-05 paperMVVB/sections/content.tex
new date version

	\caption{The resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au}. For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit. The sums of absolute residuals are shown as well. The values in brackets are the estimated standard deviation of each fit parameter.}

@@

		S[table-format = 2.1]

@@

		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{SAR}\\
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{[\%]}\\

@@

		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&6.83\\
		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&18.69\\
		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&6.48\\
		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&5.78\\

@@

		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}\\
			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}\\
		\cline{2-6}
			&\multicolumn{1}{c}{$W_\text{II}$}	&4.12(14)\tablefootmark{b}	&4.38(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&4.20\\

@@

Again, the velocity gets a special treatment with the double lognormal distribution (see Eq.~\ref{eq:double_lognormal_fit_function}), this time keeping its two components' positions constant and variing instead their balance with the SSN:	(discuss why...)
\begin{align}
	c(ssn) &= c_a \cdot ssn + c_b\,.
\end{align}
The fit result is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_b_plot.pdf}}
	\caption{Ratio of slow to fast solar wind depending on the by 3~years lagged SSN. The relation results from the velocity's double lognormal fit.}
	\label{fig:Vdbl_SSN_ratio_b_plot}
\end{figure}

@@

With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (vgl.Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}). derive value...\\

@@

error sources:\\
- extrapolation\\
- model\\

>>>>

	\caption{The resulting fit coefficients from the fitting of the lognormal function (\ref{eq:single_lognormal_fit_function}) to the shape of the solar wind parameters' frequency distributions at \SI{1}{\au}. For the velocity also the fit parameters from the double lognormal function (\ref{eq:double_lognormal_fit_function}) are given, as well as the median and mean values of the resulting velocity fit. The mean absolute errors and sums of absolute residuals are shown as well. The values in brackets are the estimated standard deviation of each fit parameter.}

@@

		S[table-format = 1.2e+2]
		S[table-format = 2.2]

@@

		\multicolumn{2}{l}{\multirow{2}{*}{Parameter}}	&\multicolumn{1}{c}{Median}	&\multicolumn{1}{c}{Mean}	&\multicolumn{1}{c}{Balance}	&\multicolumn{1}{c}{MAE}	&\multicolumn{1}{c}{SAR}\\
		\multicolumn{2}{l}{}	&\multicolumn{1}{c}{$x_\text{med}$\tablefootmark{a}}	&\multicolumn{1}{c}{$x_\text{avg}$\tablefootmark{a}}	&\multicolumn{1}{c}{$c$}	&\multicolumn{1}{c}{}	&\multicolumn{1}{c}{[\%]}\\

@@

		\multicolumn{2}{l}{Magnetic field}	&5.661(16)	&6.164(18)	&--	&5.51e-4	&6.83\\
		\multicolumn{2}{l}{Velocity}	&4.085(19)	&4.183(20)	&--	&1.80e-3	&18.69\\
		\multicolumn{2}{l}{Density}	&5.276(24)	&6.484(34)	&--	&5.49e-4	&6.48\\
		\multicolumn{2}{l}{Temperature}	&7.470(17)	&11.301(32)	&--	&8.71e-5	&5.78\\

@@

		\multirow{2}{*}{Velocity}	&\multicolumn{1}{c}{$W_1$}	&4.89(14)	&5.00(14)	&\multirow{2}{*}{0.504(62)}	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
			&\multicolumn{1}{c}{$W_2$}	&5.9089(53)	&3.72(20)	&	&\multicolumn{1}{c}{--}	&\multicolumn{1}{c}{--}\\
		\cline{2-7}
			&\multicolumn{1}{c}{$W_\text{II}$}	&4.12(14)\tablefootmark{b}	&4.38(14)\tablefootmark{b}	&\multicolumn{1}{c}{--}	&3.98e-4	&4.20\\

@@

Again, the velocity gets a special treatment with the double lognormal distribution (see Eq.~\ref{eq:double_lognormal_fit_function}), this time keeping its two components' positions constant and variing instead their balance with the SSN:	(discuss why...)
\begin{align}
	c(ssn) &= c_a \cdot ssn + c_b\,.
\end{align}
The fit result is a model in which three years after solar cycle minimum (SSN of zero) the slow solar wind has a share of almost two-thirds and decreases further with increasing SSN (see Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/Vdbl_SSN_ratio_b_plot.pdf}}
	\caption{Yearly ratio between slow to fast solar wind (threshold \SI{400}{\km\per\s} over SSN (+). Fit model ratio depending on the by 3~years lagged SSN (black line). The relation results from the velocity's double lognormal fit.}
	\label{fig:Vdbl_SSN_ratio_b_plot}
\end{figure}

@@

With $c = 0.557$ the velocity balancing parameter is of an expected value similar to that obtained from the Helios time period (the mean SSN during the Helios period was 59, this corresponds to a $c(59) = 0.53$, vgl.Fig.~\ref{fig:Vdbl_SSN_ratio_b_plot}).\\

@@

error estimation for general model and extreme value tendencies\\

error sources:\\
- extrapolation\\
- lognormal model\\
- SSN variance\\
